Quality Criteria for SKOS Vocabularies

### 2012-03-19 introduction.tex
polished background section
changed from metric to crtieria

% What does "quality" mean in this context?
Each vocabulary reflects domain- and application-specific needs and vocabulary designers often follow existing standards \cite{ISO25964-1:2011,Z39.19:2005} or apply their own hand-crafted checks (cf.,~\cite{Coronado2009}) to meet certain quality requirements. However, these requirements can differ across domains and lead to quality problems when a vocabulary is used in other environments. As a consequence, currently available vocabularies are, even though they are expressed in SKOS, often heterogeneous in terms of quality. The following examples illustrate that this can affect their applicability for tasks like query expansion, faceted browsing, clustering, or auto-completion:

@@

The goal of our work is to provide a set of quantitative quality indicators for SKOS vocabularies. They can be used by domain experts and vocabulary designers for judging the quality of existing or newly created vocabularies and provide important feedback to the overall vocabulary design process. The main contributions of this work can be summarized as follows:

@@

	\item We identified existing \textbf{quality criteria} for controlled vocabularies by examining existing guidelines and formalized them into computable \textbf{quality metrics} so that they can be implemented consistently by different tools.

	\item We implemented these metrics in the \textbf{qSKOS quality assessment tool}, which can be used as software library or command line tool.

>>>>

% What does "quality" mean in this context?
Each vocabulary reflects domain- and application-specific needs and taxonomists often follow existing standards \cite{ISO25964-1:2011,Z39.19:2005} or apply their own hand-crafted checks (cf.,~\cite{Coronado2009}) to meet certain quality requirements. However, these requirements can differ across domains and lead to quality problems when a vocabulary is used in other environments. As a consequence, currently available vocabularies are, even though they are expressed in SKOS, often heterogeneous in terms of quality. The following examples illustrate that this can affect their applicability for tasks like query expansion, faceted browsing, clustering, or auto-completion:

@@

The goal of our work to help taxonomists in judging the quality of SKOS vocabularies, by giving them a set of computable quality criteria that can identify possible quality issues and serve as quantitative indicator for the quality of a given SKOS vocabulary. In combination with the taxonomists' experience and domain expertise, these criteria provide important feedback to the overall vocabulary design process. The main contributions of this work can be summarized as follows:

@@

	\item We identified existing \textbf{quality criteria} for controlled vocabularies by examining existing guidelines and formalized them into computable \textbf{filtering functions} that identify possibly affected resources in a given SKOS vocabulary.

	\item With the \textbf{qSKOS quality assessment tool} we provide a reference implementation of these filtering functions.

### 2012-03-19 main.tex
drafted background section
changed (parts) of skos quality model to conform to RDF formal semantics; changed definition of loose concepts and recomputed tabular values.
changed from metric to crtieria

\usepackage{verbatim}
\usepackage{url}
\usepackage{amssymb}

@@

\title{Quality Metrics for SKOS Vocabularies}
\author{Christian Mader\inst{1} \and Bernhard Haslhofer\inst{2}}
\institute{
	University of Vienna, Faculty of Computer Science\\\email{christian.mader@univie.ac.at}
	\and Cornell University, Information Science\\\email{bernhard.haslhofer@cornell.edu}}

@@

The Simple Knowledge Organization System (SKOS) has become the standard model for expressing and publishing controlled vocabularies on the Web. However, SKOS vocabularies are often heterogeneous in terms of quality, which reduces their applicability across system boundaries. Here we investigate how we can support domain experts with quantitative indicators to judge the quality of SKOS vocabularies. We identified existing \textbf{quality criteria} and formalized them into computable \textbf{quality metrics}. We implemented them in the qSKOS quality assessment tool and used it to analyze the quality of existing vocabularies. The results from this analysis indicate that \todo{CM,BH}{summarize results in one sentence}.

@@

\input{metrics}

>>>>

\usepackage{url}

\usepackage{verbatim}
\usepackage{amssymb}
\usepackage{rotating}
\usepackage{booktabs}

@@

\title{Quality Criteria for SKOS Vocabularies}
\author{Christian Mader\inst{1} \and Bernhard Haslhofer\inst{2}}
\institute{
	University of Vienna, Faculty of Computer Science\\\email{christian.mader@univie.ac.at}
	\and Cornell University, Information Science\\\email{bernhard.haslhofer@cornell.edu}}

@@

The Simple Knowledge Organization System (SKOS) has become the standard model for expressing and publishing controlled vocabularies on the Web. However, SKOS vocabularies are often heterogeneous in terms of quality, which reduces their applicability across system boundaries. Here we investigate how we can support taxonomists in judging the quality of SKOS vocabularies by quality criteria that go beyond the low-level data model integrity constraints defined in the SKOS specification. Based on existing guidelines and best practices for creating controlled vocabularies, we identified existing \textbf{quality criteria}, formalized them into computable \textbf{filtering functions} that identify  affected resources and implemented them in the qSKOS quality assessment tool. We used that tool to analyze existing vocabularies and found that \todo{CM,BH}{summarize results in one sentence}.

@@

\input{criteria}
